Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
trim implementation section a bit
We don't just use NumPy for "intensive" processing but whenever it
leads to clearer code.

Our implementation guidelines emphasize writing efficient but readable code.
In particular, we focus on making the codebase easily maintainable and
understandable in order to favour external contributions. Whenever practicable,
algorithms implemented in \sklearn are thus directly written in pure Python. For
intensive numerical computations though, the library mostly relies on NumPy
vector operations, which allows for the code to remain concise, readable and
efficient. For all algorithms that cannot be easily and efficiently expressed as
NumPy operations, we rely on Cython \citep{behnel2011cython}  for writing the
critical parts and achieving decent performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are directly importable from the
Python run-time system. Examples of algorithms written in Cython include
stochastic gradient descent for linear models, some graph-based clustering
algorithms and decision trees.

>>>>

Our implementation guidelines emphasize writing efficient but readable code.
In particular, we focus on making the codebase easily maintainable and
understandable in order to favour external contributions. Whenever practicable,
algorithms implemented in \sklearn are written in Python,
using Numpy vector operations for numerical work.
This allows for the code to remain concise, readable and
efficient. For critical algorithms that cannot be easily and efficiently
expressed as NumPy operations, we rely on Cython \citep{behnel2011cython}
to achieve decent performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are directly importable from the
Python run-time system. Examples of algorithms written in Cython include
stochastic gradient descent for linear models, some graph-based clustering
algorithms and decision trees.
